Usage metrics

### 2020-12-11 inst/analysis/usage_metrics.Rmd
minor

```{r call-sites-violin-plot, echo=F}
E %>%
  group_by(ev_package) %>%
  mutate(sites=n_distinct(src_ref)) %>%
  ggplot(aes(x=ev_variant, y=sites, fill=ev_variant), na.rm=TRUE) +
  geom_violin(trim=FALSE, width=1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background=element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

>>>>

```{r call-sites-violin-plot, echo=F}
E %>% 
  select(ev_package, ev_variant, src_ref) %>%
  group_by(ev_package, ev_variant) %>%
  summarize(sites=n_distinct(src_ref)) %>%
  ggplot(aes(x=ev_variant, y=sites, fill=ev_variant), na.rm=TRUE) +
  geom_violin(trim=FALSE, width=1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background=element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  ) -> PLOT

@@

`r PLOT`
